COMPAS Race Analysis

### 2022-04-05 race compas analysis.Rmd
echo = false

```{r setup, include=FALSE}
library(reticulate)
```

```{python}
import matplotlib.pyplot as plt
import matplotlib.patches as patches
import numpy as np
import pandas as pd
import seaborn as sns

@@

```{python}
from aif360.sklearn.preprocessing import ReweighingMeta, Reweighing
from sklearn.metrics import accuracy_score, confusion_matrix, plot_roc_curve, recall_score, precision_score

@@

```{python}
plot_fair_metrics([0, 0, 0], '')
plt.show()
```

# Pre-Processing Approach
```{python}
lr = LogisticRegressionCV(solver='lbfgs')
rew = ReweighingMeta(estimator=lr, reweigher=Reweighing('race'))
rew.fit(X_train, y_train)
y_pred_REW = rew.predict(X_test)
```

```{python}
acc_REW = accuracy_score(y_test, y_pred_REW)
print(f'[Reweighting] The test accuracy of the algorithm is: {acc_REW: .2%}')
```

```{python}
cf_matrix = confusion_matrix(y_test, y_pred_REW)
make_confusion_matrix(cf_matrix, "[Reweighting]")
plt.show()
```

```{python}
metrics_per_group(y_test, y_pred_REW)
plt.show()
```

```{python}
stat_par_diff_RW = statistical_parity_difference(y_test, y_pred_REW, prot_attr='race', pos_label = 0)

@@

```{python}
from aif360.sklearn.postprocessing import CalibratedEqualizedOdds, PostProcessingMeta

>>>>

# Set Up

```{r py setup, include=FALSE}
library(reticulate)
```

```{python import, include= FALSE}
import matplotlib.pyplot as plt
import matplotlib.patches as patches
import numpy as np
import pandas as pd
import seaborn as sns

@@

```{python baseline set up, warning = FALSE, message = FALSE, echo = FALSE}
from aif360.sklearn.preprocessing import ReweighingMeta, Reweighing
from sklearn.metrics import accuracy_score, confusion_matrix, plot_roc_curve, recall_score, precision_score

@@

```{python group fairness metrics plot}
plot_fair_metrics([0, 0, 0], '')
plt.show()
```

# Pre-Processing Approach
```{python pre-processing set up, warning = FALSE, message = FALSE, echo = FALSE}
lr = LogisticRegressionCV(solver='lbfgs')
rew = ReweighingMeta(estimator=lr, reweigher=Reweighing('race'))
rew.fit(X_train, y_train)
y_pred_REW = rew.predict(X_test)
```

```{python pre-processing accuracy score} 
acc_REW = accuracy_score(y_test, y_pred_REW)
print(f'[Reweighting] The test accuracy of the algorithm is: {acc_REW: .2%}')
```

```{python pre-processing confusion matrix}
cf_matrix = confusion_matrix(y_test, y_pred_REW)
make_confusion_matrix(cf_matrix, "[Reweighting]")
plt.show()
```

```{python pre-processing metrics per group}
metrics_per_group(y_test, y_pred_REW)
plt.show()
```

```{python pre-processing statistical parity difference}
stat_par_diff_RW = statistical_parity_difference(y_test, y_pred_REW, prot_attr='race', pos_label = 0)

@@

```{python post-processing calibrated equal odds set up, warning = FALSE, message = FALSE, echo = FALSE}
from aif360.sklearn.postprocessing import CalibratedEqualizedOdds, PostProcessingMeta
